---
title: "Data Incubator Project"
author: "Shouman Das"
date: "February 4, 2019"
output: html_document
---
First we load the two data sets and useful packages. It takes a little time, as the data set is big. 
```{r, cache=TRUE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(gridExtra)
linkedin = read.csv("temp_datalab_records_linkedin_company.csv")
facebook = read.csv("temp_datalab_records_social_facebook.csv")

```
Next we do a simple summary of the interesting columns of the two datasets. 
```{r}
summary(linkedin[,c(2,3,4,5,7)])
summary(facebook[,c(2,3,4,7,8,9)])
```
To start with some exploratory plots, I pick some well-known established companies which appear in the both data sets and then I plot the timeseries data. For example, first I picked "Starbucks" and plot it's number of facebook likes and linkedin profile.
```{r,cache=TRUE}
starbucks.lkd = linkedin[linkedin$company_name=="Starbucks",c(2,5)]
starbucks.fb = facebook[facebook$username=="Starbucks",c(2,7)]

starbucks.lkd$as_of_date = as.POSIXct(starbucks.lkd$as_of_date)
starbucks.fb$time = as.POSIXct(starbucks.fb$time)

# plotting
s.lkd = ggplot(starbucks.lkd, aes(x = as_of_date, y = employees_on_platform)) +
  geom_line(size = 1, color = "blue") + xlab("Time")+ylab("Starbucks Employees")
s.fb = ggplot(starbucks.fb, aes(x = time, y = likes)) +
  geom_line(size = 1, color = "blue") + xlab("Time")+ylab("Starbucks Likes")
grid.arrange(s.lkd, s.fb, nrow = 2)
```

From the plot, we can infer that at the beginning of 2018, starbucks social media popularity didn't perform as well as the number of employees. There might be some unknown variables which has effected badly their social media presence. 

For the next plot we pick another well known company "McDonalds" which has a siginificant presence in the social media. We draw similar plot. 
```{r,cache=TRUE}
mcdonalds.lkd = linkedin[linkedin$company_name=="McDonald's",c(2,5)]
mcdonalds.fb = facebook[facebook$username=="McDonalds",c(2,7)]

mcdonalds.lkd$as_of_date = as.POSIXct(mcdonalds.lkd$as_of_date)
mcdonalds.fb$time = as.POSIXct(mcdonalds.fb$time)

# plotting
m.lkd = ggplot(mcdonalds.lkd, aes(x = as_of_date, y = employees_on_platform)) +
  geom_line(size = 1, color = "blue") + xlab("Time")+ylab("McDonald's Employees")
m.fb = ggplot(mcdonalds.fb, aes(x = time, y = likes)) +
  geom_line(size = 1, color = "blue") + xlab("Time")+ylab("McDonald's Likes")
grid.arrange(m.lkd, m.fb, nrow = 2)
```

For Mcdonald's, the employee growth and social media growth looks highly correlated. 

It would be an interesting question how this number of employees and social media popularity are correlated for other medium to small scale companies. 


